---
title: "graphsearch_timedata"
output: html_document
date: "2025-1-7"
---

To get data on how much time was spent on searching for graphs,
we can scrape the data off the time logs.

For now, I'm just going to get timing data for one parameter set.

## Collect time data from logs on the cluster

Run this block on franklin01 `nobackup2/lefrankel/f4-ratevar`.

```{julia}
using CSV
using DataFrames
```

```{julia}
path = "output/fleg_10-indls_118000-genes_100000-biall_0.0-lindist_1.25e-8-subrate"

#get all the rep dirs for the best case scenario
reps = sort!(filter!(contains(r"\d.+"), readdir(path)))

#initialize df
time_df = DataFrame(irep=Int64[], irun=Int64[], h_search= Int[], time=Float64[])

for rep in reps
  rep_int = parse(Int, rep)
  f = open("$path/$rep/graphsearch_log.txt", "r")
    for line in readlines(f)
      #check first that line contains "time:", ignore those that don't
      if contains(line, "time:")
        comma_split = split(line, ", ")
        irun = parse(Int, split(comma_split[1], ": ")[2])
        h_search = parse(Int, split(comma_split[2], ": ")[2])
        time = parse(Float64, split(split(comma_split[4], ": ")[2], " ")[1])

        push!(time_df, (rep_int, irun, h_search, time)) 

      end
    end
  close(f)
end

CSV.write("output/fleg_10-indls_118000-genes_100000-biall_0.0-lindist_1.25e-8-subrate/timingdata.csv", time_df)
```

If I were to collect this data for all parameter sets / clusters,
this script needs to be run on every cluster,  or I need to move all my scripts to 
the same cluster (problematic, would need to append, as I might have duplicate logs 
for the same rep on diff clusters).

Would also need to add columns in dataframe with `net, indls, nbiallelic, lindist, subrate`.
Would then need to combine all CSVs across clusters.

But for now, I'm not doing that. I'm just focusing on timing data for one parameter set.

## Analyze data locally

```{r}
library("readr")
library("rlang")
library("magrittr")
library("dplyr")
```

### Sanity checks

First let's check that there's 50 runs per irep/h_search combo.

```{r}
timedata = read_csv("output/timingdata.csv")

summaryireps = timedata %>%
  group_by(irep, h_search) %>%
  summarize(irep     = first(irep),
            h_search = first(h_search),
            count    = n())

summaryireps %>%
  filter(count < 50)
```

That returns an empty table. Great! No irep + h_search combos had less than 50 iruns.

And the `summaryireps` table has 300 rows, which is what we expect. (100 reps * 3 h_search values = 300 groups / rows)

### Get summary of timing data

```{r}
summary_hsearch = timedata %>%
  group_by(h_search) %>%
  summarize(h_search = first(h_search),
            count    = n(),
            avgtime  = mean(time),
            mintime  = min(time),
            maxtime  = max(time),
            sumtime  = sum(time))
```

> summary_hsearch
 A tibble: 3 × 6
  h_search count avgtime mintime maxtime sumtime
     <dbl> <int>   <dbl>   <dbl>   <dbl>   <dbl>
1        0  5000    2.47   0.779    5.47  12340.
2        1  5000   11.8    1.49    69.2   59182.
3        4  5000  122.     2.67   697.   611811.

Time here is in *minutes!* The total amount of time across all three
h_search vals is 12340+59182+611811 = 683,333 minutes.